### 2014-10-16 excersice 1/main.tex

\section*{Q3}
\begin{enumerate}
\item % a 
\label{itm:3a}
The amount of cycles will be the following for MSI:
\texttt{
  \\Proc1: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr
  \\Proc2: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr
  \\Proc3: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr
  \\Proc4: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr 
}
\[4\times(40+(20+10+1)+1) = 288\]
and for MESI:
\texttt{
  \\Proc1: LvL2Rd + Wr + Wr
  \\Proc2: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr
  \\Proc3: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr
  \\Proc4: LvL2Rd + (LvL1RdX + BusUP + Wr) + Wr 
}
\[(40+1+1)+3\times(40+(20+10+1)+1) = 258\]
where the difference is due to the first processor going to the E state instead of the S state and thereby saves 30 cycles when it then wants to write. There are no Snoops done as we only care about the cycles wasted in the current cache.

\item % b 
The amount of trafic that gets generated for MSI based on the sequences in (a)):
\[4\times(38B+38B+10B) = 344B\]
and for MESI:
\[38B+3\times(38B+38B+10B) = 296B\]
\end{enumerate}

>>>>

\section*{Q3}
\begin{enumerate}
\item % a 
\label{itm:3a}
\textcolor{red}{
The amount of cycles will be the following for MSI:
\texttt{
  \\Proc1: (Snoop + LvL2Rd + Rd) + (BusUP + Snoop + Wr) + Wr
  \\Proc2: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr
  \\Proc3: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr
  \\Proc4: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr 
}
}
\textcolor{red}{
\[(5+40+1)+(10+5+1)+1+3\times((5+20+1)+(10+5+1)+1) = 192\]
and for MESI:
\texttt{
  \\Proc1: (Snoop + LvL2Rd + Rd) + Wr + Wr
  \\Proc2: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr
  \\Proc3: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr
  \\Proc4: (Snoop + LvL1Rd + Rd) + (BusUP + Snoop + Wr) + Wr 
}
}
\textcolor{red}{
\[(5+40+1)+1+1+3\times(5+20+1+(10+5+1)+1) = 177\]
where the difference is due to the first processor going to the E state instead of the S state and thereby saves 15 cycles when it then wants to write by not needing to emit a busupgrade and or snoop the bus. I assume that the bus upgrades does not include any snoop.}

\item % b 
\textcolor{red}{
The amount of trafic that gets generated for MSI based on the sequences in (a)):
\[4\times(38B+10B) = 192B\]
and for MESI:
\[38B+3\times(38B+10B) = 182B\]
}
\end{enumerate}
